Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2022-12-21 paper-1/manuscript.tex
Editing

When a neuron's membrane potential reached the firing threshold $v_\theta$, a spike was emitted, and the potential was clamped to $V_m = V_{reset} = -74$~mV for a fixed refractory period of 3~ms (excitatory neurons). Inhibitory neurons were modeled as fast-spiking cells with a refractory period of 2~ms and a constant firing threshold $v_\theta = \theta_0 = -54$~mV \refp{Mensi2012-au}. In contrast, excitatory neurons were modeled with threshold adaptation (TA) as in \cite{Teeter2018-iz}, following
\begin{align}
    v_\theta &= \theta_0 + V_{TA}(t) \nonumber \\
    \tau_{\theta} \frac{dV_{TA}}{dt} &= -V_{TA} + \hat{\theta} \delta(t - \hat{t}) \label{eqn-TA}
\end{align}
with increment $\hat{\theta} = 1$~mV and decay time constant $\tau_{\theta} = 1$~s \refp{Pozzorini2015-ei}.

>>>>

When a neuron's membrane potential reached the firing threshold $v_\theta$, a spike was emitted, and the potential was clamped to $V_m = V_{reset} = -74$~mV for a fixed refractory period of 3~ms (excitatory neurons). Inhibitory neurons were modeled as fast-spiking cells with a refractory period of 2~ms and a constant firing threshold $v_\theta = \theta_0 = -54$~mV \citep{Mensi2012-au}. In contrast, excitatory neurons were modeled with threshold adaptation (TA) as in \cite{Teeter2018-iz}, following
\begin{align}
    v_\theta &= \theta_0 + V_{TA}(t) \nonumber \\
    \tau_{\theta} \frac{dV_{TA}}{dt} &= -V_{TA} + \hat{\theta} \delta(t - \hat{t}) \label{eqn-TA}
\end{align}
with increment $\hat{\theta} = 1$~mV and decay time constant $\tau_{\theta} = 1$~s \citep{Pozzorini2015-ei}.
